COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-05-13 main.tex
Add new bump vs dip diagnostic figure

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/bump_dip_diag.png}
    \caption{The presence of a dip or bump near the resonances can be used to constrain the mass and eccentricity
    of the perturbing planet. A simultaneous dip and the 2:1 MMR, combined with a bump at the 3:1 MMR can be
    used to place even more restrictive constraints.\label{fig:bump_dip_diag}}
\end{center}
\end{figure}

>>>>

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/bump_dip_diag.png}
    \caption{The presence of a dip or bump near the resonances can be used to constrain the mass and eccentricity
    of the perturbing planet. The color scale indicates the relative strength of the features, while the dashed lines
    indicate boundaries in parameter space where a dip or a bump will be produced at the resonance.\label{fig:bump_dip_diag}}
\end{center}
\end{figure*}
